Learning Discrete Bayesian Networks from Continuous Data

### 2017-05-08 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
JAIR & Approx paragraph

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
  %!PS-Adobe-3.0 EPSF-3.0
  %%BoundingBox: 19 19 221 221
  %%CreationDate: Mon Sep 29 1997
  %%Creator: programmed by hand (JK)
  %%EndComments
%  gsave
%  newpath
%    20 20 moveto
%    20 220 lineto
%    220 220 lineto
%    220 20 lineto
%  closepath
%  2 setlinewidth
%  gsave
%    .4 setgray fill
%  grestore
%  stroke
%  grestore
%\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{BOONDOX-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{tabularx}

@@

@@

\author{Yi-Chun Chen           \and
        Tim A. Wheeler         \and
        Mykel J. Kochenderfer
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Yi-Chun Chen \at
              Institute of Computational and Mathematical Engineering, Stanford University \\
              \email{yichunc@stanford.edu}
           \and
              Tim A. Wheeler \at
              Department of Aeronautics and Astronautics, Stanford University\\
              \email{wheelert@stanford.edu}
           \and
              Mykel J. Kochenderfer \at
              Department of Aeronautics and Astronautics, Stanford University\\
              \email{mykel@stanford.edu}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

Learning Bayesian networks from raw data can help interpret the variable iterrelationships and structure without relying on field-specific experts.
While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
Thus, continuous variables are often discretized when learning a Bayesian network.
However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
Empirical demonstrations show that the proposed method is superior to the established minimum description length algorithm.
In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.

@@

\keywords{Discretization \and Bayesian Network \and Continuous Variable}
  % \PACS{PACS code1 \and PACS code2 \and more}
  % \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\noindent
where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval. Table \ref{table:data_demo} and \ref{table:data_demo_2} demonstrate variable assignments for an example dataset.

%For example, Table \ref{table:data_demo} is a dataset that mixes continuous variable $\cX$ and discrete variables $A$ and $B$. Data samples are arranged in an ascending order of $\cX$. Therefore, $n = 10$, $m =6$, $\cx_{1:10} = \curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $, and  $\cu_{1:6} = \curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$. The corresponding index $s$ of $\cu$ in $\cx$ is $s_{1:6} = \curly{1,3,6,7,9,10}$. In addition, a three-interval discretization policy $\Lambda^0_{\cX}$ with edges $e_1 = 1.55$ and $e_2 = 4.65$ can be represented as
%\begin{equation}
%\Lambda^0_{\cX} = \anglebrackets{\lambda_1 = 3 , \lambda_2 = 9, \lambda_{3} = 10 } \equiv \anglebrackets{\gamma_1 = 3, \gamma_2 = 6, \gamma_3 = 1} \text{.}
%\end{equation}

\begin{table}[ht]
  \centering
  \caption{
    An example dataset used to demonstrate the variables defined in Section \ref{subsec:disc_policy}. Rows are assignments to continuous variable $\cX$ and discrete variables $A$ and $B$.
  }
  \input{Table0.tex}
  \label{table:data_demo}
  \bigskip
  \centering
  \caption{
    Assignments for variables defined in Section~\ref{subsec:disc_policy} according to the dataset in Table~\ref{table:data_demo}.
  	Note that $\Lambda^{\text{ex}}_{\cX}$ is an example of a valid discretization policy. Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indices $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indices $\anglebrackets{}_{\gamma}$.
  }
	\begin{tabular}{cc}
		\toprule
		Variable &  Value \\
		\midrule
		$n$ &  \num{10} \\
		$m$ &  \num{6} \\
		$\cx_{1:10}$ & $\curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $\\
		$\cu_{1:6} $ & $\curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$\\
		$s_{1:6}$ & $\curly{1,3,6,7,9,10}$\\
		$\Lambda^{\text{ex}}_{\cX}$ & $\anglebrackets{1.55,4.65}_{e}$, $ \anglebrackets{3 ,9,10}_{\lambda}$, $\anglebrackets{3, 6, 1}_{\gamma} $\\
		\bottomrule
	\end{tabular}
  \label{table:data_demo_2}
\end{table}

@@

A Bayesian network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ whose nodes are the random variables and a conditional probability distribution for each node given its parents.
The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
The children of node $X_i$ are denoted $\Ch_{X_i}$.

When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ associated with the $i$th child.
%The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.

@@

\begin{small}
\begin{equation}
  \label{eq:p_M}
  P(\Lambda) = \prod_{i=1}^{k-1}
    \brock{
      1 - \exp\paren{
        - L \cdot \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
    \prod_{i=1}^{k}
	\brock{
    \exp\paren{
      -L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1}}
    }\text{.}
\end{equation}
\end{small}

@@

The two factors on the right hand side come from the third principle: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
According to the fourth prior, these distributions are independent from each other, and one can thus take their product.
If $\bm{S}_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to

@@

Precomputation reduces runtime.
Hence, $h(u,v)$ is computed first for each interval $\gamma_q$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:

@@

The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the number of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$.

@@

% \subsection{Approximation}

% Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{\paren{L'}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
% This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
% The approximation replaces the dominator of the last factor in Equation~\ref{eq:likelihood_one} with

% \begin{equation}
% {\frac{{\gamma_i}!}{ {n^{\text{P}}_{i,1} !} {n^{\text{P}}_{i,2} !} \cdots {n^{\text{P}}_{i,J_\text{P}} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
% \end{equation}

% \noindent
% where $P_r$ is the $r$th parent variable, $J_{p_r} = \| P_r\|$, and ${n^{(P_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$. Note that $\gamma_i = \sum_j {n^{(P_r)}_{i,j}}$ for all $r$.
% The approximated objective function is

% \begin{small}
%   \begin{equation}
%   \label{eq:opt_prob_approx}
%   \begin{aligned}
%     & \sum_{i=1}^{k-1}
%      - \ln
%       \paren{
%         1 - \exp
%         \paren{
%           - L \cdot  \frac{
%                            \cx_{\lambda_i +1} - \cx_{\lambda_i}
%                          }{
%                            \cx_n - \cx_1
%                           }
%         }
%       }
%         + \sum_{i=1}^{k}
%         L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
%     & \sum_{i=1}^{k} \brock{
%     \ln{{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}
%     +{ \ln \paren{
%           \frac{
%             {\gamma_i}!
%           }{ \sum_{r=1}^{n_p}
%             {n^{({P_r})}_{i,1}}! \; {n^{({P_r})}_{i,2}}! \; \cdots \; {n^{({P_r})}_{i,J_{P_r}}}!
%           }
%         }}
%     } \\
%     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_\bm{S}} \brock{
%     { \ln
%             {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
%       +
%       \ln \paren{ {
%             \frac{
%               {n^{(j)}_{i,\ell}}!
%             }{
%               {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
%             }
%           }
%           } }
%   \end{aligned}
%   \end{equation}
% \end{small}

% The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}$.
% It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.

% The approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
% For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are

% \begin{small}
%   \begin{equation}
%   \begin{aligned}
%   \label{eq:example_approx}
%    \sum_{i=1}^k & \left\lbrace   \left[ \ln{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \ln \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right. \right.\\
%   & \left.  \ln{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \ln \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
%   &  \left. \left[  \ln {{\gamma_{i} + J_\text{P} - 1}\choose{J_\text{P}-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
%   \end{aligned}
%   \end{equation}
% \end{small}

% In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
% In this case the child variables have greater effect on the optimal discretization than the parent variables, even though the number of child and parent variables are the same.
% However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced.
% This is due to the additional influence of $S_2$ on $C_2$.
% This phenomenon arrises because the Bayesian method, but with and without the heuristic, incorporates graph structure when discretizing continuous variables.

% \begin{figure}[ht]
%   \centering
%   \begin{tabular}{cc}
%     \input{graph2_left}
%     \end{tabular}
%     \hspace{5em}
%     \begin{tabular}{cc}
%     \input{graph2_right}
%   \end{tabular}
%   \caption{Two example networks}
%   \label{fig:example_networks}
% \end{figure}

@@

\begin{table}[ht]
	\centering
	\caption{
		Discretization results for several datasets.
    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
    The Bayesian method consitently has higher likelihood.
	}
  \resizebox{\textwidth}{!}{
	 \input{Table3_2.tex}
  }
	\label{table:more_data_set}
\end{table}

@@

% Non-BibTeX users please use
%\begin{thebibliography}{}
\bibliographystyle{spbasic}
\bibliography{my_bib}

@@

%\subsection*{Results on More Datasets}
%
%In this subsection, six additional datasets \citep{Lichman_2013} are tested as a supplementary to Section \ref{sec:experiments}. For each dataset, a comparison between the proposed method and MDL-principle method has been made. The discretization results of two methods are shown in terms of discretization edges and likelihood on a given network structure, which is obtained by uniform discretization and K2 structure learning, same as in Section \ref{sec:experiments}. The results still indicates that the proposed method outperforms than the MDL-principle discretization, in which the latter suffers from low number of discretization edges.
%
%\subsubsection*{Dataset: Seeds}
%
%The Seeds data sets contains variables related to the shape of seeds of two species. The dataset has 210 samples over eight variables. Only variable $H$ is discrete-valued. The discretization methods are tested on the fixed network structure: $\Pa_A = \curly{\emptyset}$, $\Pa_B = \curly{ A }$, $\Pa_C = \curly{B, E}$, $\Pa_D = \curly{A,B}$, $\Pa_E = \curly{B}$, $\Pa_F = \curly{A,H}$, $\Pa_G = \curly{B,D,H}$, and $\Pa_H = \curly{B}$. This network is obtained by first uniformly discretizing each variable by two intervals then running K2 structure learning.
%
%\begin{table}[ht]
%	\centering
%	\caption{
%		The discretization policies for the Seeds dataset with a fixed structure.
%		The methods have the same discretization for variable $G$, close discretization edge for variable $F$, and the log-likelihood for the Bayesian method is better than that for the MDL method.
%	}
%	\input{Table6.tex}
%	\label{table:auto_disc_seeds}
%\end{table}
%
%\subsubsection*{Dataset: Glasses}
%
%\subsubsection*{Dataset: Heart}
%
%\subsubsection*{Dataset: Liver Disorder}
%
%\subsubsection*{Dataset: Indian Liver Patient}
%
%\subsubsection*{Dataset: Banknote authentication}
\end{document}
% end of file template.tex

>>>>

\RequirePackage{fix-cm}

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{BOONDOX-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{tabularx}

@@

%\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
%\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
%{Chen, Wheeler, \& Kochenderfer}
%\firstpageno{25}

@@

\author{\name Yi-Chun Chen \email yichunc@stanford.edu \\
	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Tim A. Wheeler \email wheelert@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA\\
	\AND
	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA}
%\authorrunning{Short form of author list} % if too long for running head

@@

Learning Bayesian networks from raw data can help interpret the variable interrelationships and structure without relying on field-specific experts.
While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
Thus, continuous variables are often discretized when learning a Bayesian network.
However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
Empirical demonstrations show that the proposed method is superior to the established minimum description length algorithm.
In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.

@@

\end{abstract}

@@

\noindent
where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval. Both $\lambda_{1:k}$ and $\gamma_{1:k}$ representations will be used in the following content. The former makes the dynamic programming algorithm more succinct, and the latter makes equations more compact when calculating data instantiations. Table \ref{table:data_demo} and \ref{table:data_demo_2} demonstrate variable assignments for an example dataset.

\begin{table}[ht]
  \centering
  \caption{
    An example dataset used to demonstrate the variables defined in Section \ref{subsec:disc_policy}. Rows are assignments to continuous variable $\cX$ and discrete variables $A$ and $B$.
  }
  \input{Table0.tex}
  \label{table:data_demo}
  \bigskip
  \centering
  \caption{
    Assignments for variables defined in Section~\ref{subsec:disc_policy} according to the dataset in Table~\ref{table:data_demo}. Note that $\Lambda^{\text{ex}}_{\cX}$ is an example of a valid discretization policy. Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indices $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indices $\anglebrackets{}_{\gamma}$. That is to say, in the edge representation, $e_1 = 1.55$ and $e_2 = 4.65$. In the $\lambda_{1:k}$ representation, $\lambda_1 = 3$, $\lambda_2 = 9$, and $\lambda_3 = 10$. In the $\gamma_{1:k}$ representation, $\gamma_1 = 3$, $\gamma_2 = 6$, and $\gamma_3 = 10$. Furthermore, one can check that $\lambda_1 = \gamma_1 = 3$, $\lambda_2 - \lambda_1 = \gamma_2$, and $\lambda_3 - \lambda_2 = \gamma_2$.

  }
	\begin{tabular}{cc}
		\toprule
		Variable &  Value \\
		\midrule
		$n$ &  \num{10} \\
		$m$ &  \num{6} \\
		$\cx_{1:10}$ & $\curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $\\
		$\cu_{1:6} $ & $\curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$\\
		$s_{1:6}$ & $\curly{1,3,6,7,9,10}$\\
		$\Lambda^{\text{ex}}_{\cX}$ & $\anglebrackets{1.55,4.65}_{e}$, $ \anglebrackets{3 ,9,10}_{\lambda}$, $\anglebrackets{3, 6, 1}_{\gamma} $\\
		\bottomrule
	\end{tabular}
  \label{table:data_demo_2}
\end{table}

@@

A Bayesian Network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ containing one node for each variable $X_i$, and each node is associated with a conditional probability distribution $P(x_i \mid \parents(i))$ for the node given its parents in $G$. The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
The children of node $X_i$ are denoted $\Ch_{X_i}$.

When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ associated with the $i$th child. Note that the set of variables $P \cup C \cup \bm{S}$ is called Markov blanket.  
%The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.

@@

\begin{small}
\begin{equation}
  \label{eq:p_M}
  P(\Lambda) \propto \prod_{i=1}^{k-1}
    \brock{
      1 - \exp\paren{
        - L \cdot \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
    \prod_{i=1}^{k}
	\brock{
    \exp\paren{
      -L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1}}
    }\text{.}
\end{equation}
\end{small}

@@

Both factors on the right hand side come from the third principle: all distributions of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
According to the fourth prior, these distributions are independent from each other, and one can thus take their product.
If $\bm{S}_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to

@@

Precomputation reduces runtime.
Hence, $h(u,v)$ is computed first for each interval $\gamma_q = \gamma_q^{(u,v)}$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:

@@

The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the number of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$. The $n^2$ factor in the runtime comes from the fact that both $x_u$ and $x_v$ have to run over all possible values of $\cX$, which has $n$ instantiations.

@@

@@

\begin{table}[ht]
	\centering
	\caption{
		Discretization results for several datasets.
    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
    The Bayesian method consistently has higher likelihood.
	}
  \resizebox{\textwidth}{!}{
	 \input{Table3_2.tex}
  }
	\label{table:more_data_set}
\end{table}

Finding optimal discretization policy to \cref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables. The runtime issue becomes more severe if one adapts the MDL approach instead of the proposed Bayesian method in this paper. Thus, approximation approaches are reasonable alternatives, and one possibility is the greedy heuristic \cite{Friedman_1996}. Other approximation methods to dynamic programming are also applicable to solve \cref{eq:opt_prob}

@@

% Non-BibTeX users please use
%\begin{thebibliography}{}

@@

\vskip 0.2in
\bibliography{my_bib}
\bibliographystyle{theapa}

\end{document}
% end of file template.tex
